Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-20 chapters/paper2.tex
Changes 1. Updated aim 1 with first person wording 2. Updated aim 2 with first person wording and modified conclusion 3. Updated aim 3 with full size conclusion

This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
symmetry axis, stabilize bijel templates. Magnetic fields applied to bijels made without a magnetic field reveal anisotropic bijel formation, 
with microstructure evolution dependent on particle reordering at the interface, quantified using the six-fold 
Steinhardt order parameter $\langle Q6 \rangle$.

We further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
configurations of the particle monolayers dictates the extent of microstructure evolution if the applied field is increased in the direction of 
the existing order. Additionally, applying and removing a 
magnetic field results in distinct microstructural properties and timescales, highlighting the importance of processing history. These findings 
demonstrate how magnetic fields, combined with anisotropic particle-stabilized bijels, enable on-demand microstructure switching for potential applications.

@@

We begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
particle volume fraction of $\phi_p = 0.1$. We only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
for both systems. Therefore we expect that the qualitative trends between prolate and oblate particles will be matched. I select prolate particles
as they are more readily synthesizable in experiments.

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. I observe that the domain size increases as we 
    increase the applied magnetic field strength. However, upon decrease of the applied field strength the microstructure does not return to its previous value,
    demonstrating microstructure hysteresis.} 
    \label{fig:hysteresis_curve} 
\end{figure}

@@

This behavior is also observed in past work investigating the shape deformation of particle stabilized emulsions under 
electric fields. \cite{cui_stabilizing_2013} Cui et al. demonstrated that the particles unjammed and rejammed into a new kinetically arrested state resulting in
the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are in
in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while we use ellipsoidal particles. Additionally,
we also observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
In the following sections, I investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by oblate and prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The first and third row detail the microstructure evolution for oblate and prolate particle stabilized bijels with no applied field while the second and fourth rows show bijels stabilized by oblate and prolate particles respectively with a field strength of $\bar{B} = 1$ applied. Particle reorientation to the direction of the field can be seen upon application of the magnetic field, resulting in microstructure changes driven through domain coarsening until the particles jam. We see similar behavior in bijels stabilized by oblate particles upon application of the magnetic field.}
\label{fig:microstructure_viz-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_on.png} 
\caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the particle at different magnetic field strengths, $\bar{B}$, and the nematic order parameter $S$ in lines. We quantify the domain size and ordering of the particles, and show that the change in both parameters are correlated with the strength of the applied magnetic field.} 
\label{fig:domain_size-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/domain_size_aniso-field_on.png} 
\caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
         stabilized with magnetically responsive oblate and prolate ellipsoids. We see that upon application of the field, bijels stabilized with prolate 
         particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size 
         perpendicular to the applied field, $L_{\perp}$ decreases. The opposite is true for bijels stabilized with oblate particles. The tortuosity data 
         demonstrate that as the domain size increases, the tortuosity decreases and vice versa.} 
\label{fig:domain_size_aniso-field_on} 
\end{figure}

From Figure \ref{fig:domain_size_aniso-field_on}, domain size anisotropy is observed upon application of the field for both
particle morphologies. I also see some domain anisotropy with no applied field, which increases upon application of the magnetic field.
The directional domain sizes, $L_{\perp}$ and $L_{\parallel}$ increase by 73\% and 7\%\ respectively for oblate particles and
10\% and 44\% respectively for oblate particles. The axes that coarsens the most is consistent with past work, explained through the
directions particles reorient in response to the applied magnetic field. As particles unjam and rejam at the interface due to reorientating 
to the magnetic field, they adopt direction specific surface coverages which manifest as anistropic domains upon jamming. In Figure 
\ref{fig:domain_size_aniso-field_on}, we demonstrate that the application of the magnetic field changes the domain size.

@@

In Figure \ref{fig:particle_viz-field_on}, I see the initial configuration of particles at the monolayer show that the orientations are random and that the 
particles tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field direction. With no applied field,
I see that the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
as identified in Gunther et al. \cite{gunther_timescales_2014} I observe that for bijels stabilized by prolate ellipsoids, we see the adoption of orientational order
to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
with other particles differ upon application of the magnetic field. The particles would prefer to lie flat on the interface to minimize the interfacial energy of 
adsorption onto the interface. Changes in the local arrangement arise from the unjamming and rejamming process upon application of the magnetic field. These differences 
in the orientational and interfacial ordering can be characterized to understand how each respective interaction force changes as a function of time.

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.3]{../figures/results/paper2/interface_angle-nint-field_on.png} 
\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q6 \rangle)$ on the left and right respectively, 
         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application 
         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly between oblate and prolate ellipsoids 
         indicating that the dynamics for both particle morphologies differ. We also observe magnetic field dependence in each property for both particle types, 
         suggesting that these changes are driven primarily through the change in the applied field strength.} 
\label{fig:interface_angle-nint-field_on} 
\end{figure}

From Figure \ref{fig:interface_angle-nint-field_on}, we identify that prolate and oblate particles respond differently at the interface. For
bijels stabilized by oblate ellipsoids, I characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
before it reduces slightly and begins to increase once again. The initial starting value of $\langle \psi \rangle$ indicates the
particles are lying close to flat on the interface, before they begin to tilt out of the interface when the magnetic field is applied. Then,
$\langle \psi \rangle$ plateaus as the interface begins to move in response to the tilting particle at the interface. This is caused by the
large adsorption energy of the particles at the interface of the bijel, caused by high surface tension. Finally, the particles jam in place,
locking the interface at an angle to the particle. We see the rate of increase in $\langle \psi \rangle$ at early stages and the time spent
in the plateau increase with a larger applied magnetic field. The final angle at the interface is also dependent upon the applied field
strength.

When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
begins at $10 ^{\circ}$.We see $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
$\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
small compared to bijels stabilized with oblate particles. We visualize this process by color coding snapshots of the particle monolayer at the initial
and final timesteps of bijels stabilized by prolate particles with a field strength of $\bar{B} = 1$ applied.

@@

I can also do the same for $\langle \psi \rangle$ and
$\langle Q6 \rangle$. A timescale derived from
$\langle \psi \rangle$ named $\tau_{\langle \psi \rangle}$
represents the capillary timescale between the interface and the
particle. Given the shape of the plot, we assign the
$\tau_{\langle \psi \rangle}$ to be the time when the first minimum of
$\langle \psi \rangle$ is observed for prolate particles and the first
maximum for oblate particles. A timescale derived from
$\langle Q6 \rangle$, named $\tau_{\langle Q6 \rangle}$ is also
calculated which represents a timescale of local particle rearrangement.
We define $\tau_{\langle Q6 \rangle}$ as the time when
\(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
minimum of $\tau_{\langle Q6 \rangle}$ for the oblate particles. I
omit \(\bar{B} = 0\) as previous results have identified the domain size
changes observed there. I then plot the average domain size $L$
against time rescaled with these three timescales in Figure
\ref{fig:domain_size-field_on-scaled}.

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/domain_size-field_on-scaled.png} 
\caption{Plots of domain size with different timescales. The top and bottom row represent the average domain size for bijels stabilized with oblate and prolate particles respectively. The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, $\tau_S$. The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$. The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$. We show that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance of the particles during rearrangment at the interface.} 
\label{fig:domain_size-field_on-scaled} 
\end{figure}

In Figure \ref{fig:domain_size-field_on-scaled}, the left plot plots the
average domain size against time rescaled using $\tau_S$. The
the domain sizes do not collapse onto a single line, which is expected
if we want to explain the dynamics using the nematic order parameter.
This confirms the observation made above that the dynamics do not only
depend on the reorientation of particles to the field. The middle plot
demonstrates the average domain size against time rescaled using
$\tau_{\langle \psi \rangle}$. There is good agreement
between all simulations for prolate particles, although the point when
$\frac{t}{\tau_{\langle \psi \rangle}} = 1$ lies when the domain size
transition has started. However for oblate particles this
timescale does not describe the dynamics well.

@@

The hysteresis curve in Figured \ref{fig:hysteresis_curve} shiows that the microstructure change at higher
field strengths began to reduce with each subsequent field strength
jump, suggesting that the ordering of the particles is linked to the
domain size change observed. In the previous section, I saw that domain
size changes in bijels after jamming are constrained by magnetic field
driven local rearrangement of the particle monolayer. In this section,
I explore how pre-existing order in the particles affect the degree of
domain size change observed. We apply fields of strength
$\bar{B}_{template} = 0, 0.2, 0.5, 1$ during phase separation to
create bijels stabilized with ellipsoidal particles with pre-existing
particle order. I then apply a field strength of $\bar{B}_z = 1$ and
observe the time evolution of the system for $t = 10^5$ timesteps. I
simplify my nomenclature here for brevity. For example,
$\bar{B}_z: 0.0 \rightarrow 1.0$ represents a bijel made with no
field, and a field of $\bar{B}_z = 1.0$ applied during the simulations conducted here. 
I begin by visualizing the microstructure
changes experienced by bijels simulated with pre-existing particle order
in Figure \ref{fig:microstructure_viz-field_up}.

@@

In Figure \ref{fig:domain_size-field_up}, I define the difference
between the final and initial magnetic field strengths as
$\Delta \bar{B}$. The onset of microstructural response is observed to
be $\Delta \bar{B}$-dependent, indicating that a stronger driving
force is required to induce structural reorganization. Additionally, the
extent of microstructural change is also correlated with
$\Delta \bar{B}$, where $\Delta \bar{B} = 1$ results in average
microstructural variations of 5\% and 2\% for oblate and prolate
particles, respectively which decreases as $\Delta \bar{B}$ decreases.
We further characterize the relationship between $\Delta \bar{B}$ and
nematic order, showing that an increase in \(S\) correlates with
$\Delta \bar{B}$. This suggests that changes in domain size are
intrinsically linked to the initial particle ordering within the system.
These findings indicate that characteristic length scale evolution is
dependent on both aspect ratio and field strength variation,
highlighting the role of particle alignment in governing domain
coarsening dynamics. To further quantify the anisotropic microstructural
evolution, I define the relative change in domain size as
$\Delta L = \frac{L_{f} - L_{i}}{L_{i}}$, where $L$ represents
either $L_{\perp}$ or $L_{\parallel}$. The same formulation is
applied to the tortuosity in the respective directional components. I
do this to characterize the $\Delta \bar{B}$-dependent changes
observed in the domain anisotropy. The results are presented in Figure
\ref{fig:domain_size_aniso-field_up}.

\begin{figure} 
\centering 
\includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_up.png} 
\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with 
         oblate and prolate ellipsoidal particles starting at different particle orders. I plot these results against the change in the applied field 
         strength, $\Delta B$. We show that the anisotropic domain size is inversely correlated to the tortuosity. We see that $L_{perp}$ changes for 
         a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.} 
\label{fig:domain_size_aniso-field_up} 
\end{figure}

From Figure \ref{fig:domain_size_aniso-field_up}, we see that domain
size anisotropy is observed upon increasing the applied field
application of the field for both particle morphologies. I also see
some domain anisotropy with no applied field, which increases upon
application of the magnetic field. The directional domain sizes,
$L_{\perp}$ and $L_{\parallel}$ increase by $73\%$ and $7\%$
respectively for oblate particles and $10\%$ and $44\%$ respectively
for prolate particles. The axes that coarsens the most is consistent
with past work, explained through the directions particles reorient in
response to the applied magnetic field. The
tortuosity of the bijel is initially around $\tau \approx 1.5$,
consistent with simulations of the diffusive tortuosities of gyroid
structures using Lattice Boltzmann simulations.
\cite{luo_macroscopic_2020} Upon application of the field,
$\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
increases. Consistent with past work, an increase in the domain size sees a decrease in
tortuosity in that direction. \cite{karthikeyan_formation_2024}. The results show that the
tortuosity of the bijel is noticeably affected by the application of
magnetic fields.

@@

In Figure \ref{fig:particle_viz-field_up}, I see the effect of the
application of the magnetic field on the monolayer. The initial
configuration of particles at the monolayer show that even at initial
configuration of run $\bar{B}: 0.2 \rightarrow 1$, most particles are
oriented towards the field. Upon increasing the field strength to
$\bar{B} = 1$, all particles shown can be seen to be ordered to the
field, matching the results for the nematic order parameter shown in
Figure \ref{fig:domain_size-field_up}. We also observe the alignment of
the long axis of the particles to the magnetic field, demonstrating the
origin of the microstructure anisotropy. To understand how the particle
reorientation at the interface causes microstructure reorientation I
quantify the average interface angle, $\langle \psi \rangle$ and the
local interface order of the material, $\langle Q6 \rangle$ in Figure
\ref{fig:interface_angle-nint-field_up}.

@@

Figure \ref{fig:interface_angle-nint-field_up} shows that
prolate and oblate particles respond differently at the interface upon application of a magnetic field
even with pre-existing ordering of the particles. I
show that there are three time evolution trends for
$\langle \psi \rangle$ and $\langle Q6 \rangle$ for both oblate and
prolate particles despite the differences in the initial state of the
particles. In oblate particles $\langle \psi \rangle$ begins closer to
$20 ^{\circ}$ as the axis of symmetry lies close to the interface
normal. For bijels experiencing a field strength history of
$\bar{B}: 0 \rightarrow 1$ and $\bar{B}: 0.2 \rightarrow 1$,
$\langle \psi \rangle$ increases, plateaus and increases again before
plateauing again. This is indicative of particles tilting at the
interface, before interfacial capillary interactions ``pause'' particle
reorientation before the applied magnetic field begins to cause
particles to tilt out of the interface. We see similar trends for bijels
stabilized by prolate particles. $\langle \psi \rangle$ begins near
$11 ^{\circ}$. We see a decrease before reorientation ceases, and
finally $\langle \psi \rangle$ increases again.

>>>>

This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
coupled with Molecular Dynamics, I simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
symmetry axis, stabilize bijel templates. Magnetic fields applied to bijels made without a magnetic field reveal anisotropic bijel formation, 
with microstructure evolution dependent on particle reordering at the interface, quantified using the six-fold 
Steinhardt order parameter $\langle Q6 \rangle$.

I further assess how initial microstructure influences structural changes, showing that the difference in order between initial and final 
configurations of the particle monolayers dictates the extent of microstructure evolution if the applied field is increased in the direction of 
the existing order. Additionally, applying and removing a 
magnetic field results in distinct microstructural properties and timescales, highlighting the importance of processing history. These findings 
demonstrate how magnetic fields, combined with anisotropic particle-stabilized bijels, enable on-demand microstructure switching for potential applications.

@@

I begin our investigation by characterizing the microstructure changes observed on bijels stabilized with prolate ellipsoids with a 
particle volume fraction of $\phi_p = 0.1$. I only focus on one system here as the mechanism for stimuli response shown in Aim 1 is identical
for both systems. Therefore I expect that the qualitative trends between prolate and oblate particles will be matched. I select prolate particles
as they are more readily synthesizable in experiments.

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper2/hysteresis_curve.png} 
    \caption{Plot of the hysteresis curve of a bijel stabilized by magnetically responsive prolate particles. I observe that the domain size increases as I 
    increase the applied magnetic field strength. However, upon decrease of the applied field strength the microstructure does not return to its previous value,
    demonstrating microstructure hysteresis.} 
    \label{fig:hysteresis_curve} 
\end{figure}

@@

This behavior is also observed in past work investigating the shape deformation of particle stabilized emulsions under 
electric fields. \cite{cui_stabilizing_2013} Cui et al. demonstrated that the particles unjammed and rejammed into a new kinetically arrested state resulting in
the droplet being elongated in the direction of the applied field. This suggests that the particles at the interface of magnetically responsive bijels are in
in a kinetically trapped configuration. Cui et al. used spherical particles in their emulsion response experiments while I use ellipsoidal particles. Additionally,
I also observe in Figure \ref{fig:hysteresis_curve} that the response of the bijel is dependent upon the field strength applied.
In the following sections, I investigate the impact of magnetic field strength and the initial ordering of the particle monolayer on the observed stimuli response.

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by oblate and prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The first 
         and third row detail the microstructure evolution for oblate and prolate particle stabilized bijels with no applied field while the second and fourth rows show 
         bijels stabilized by oblate and prolate particles respectively with a field strength of $\bar{B} = 1$ applied. Particle reorientation to the direction of the 
         field can be seen upon application of the magnetic field, resulting in microstructure changes driven through domain coarsening until the particles jam. I see 
         similar behavior in bijels stabilized by oblate particles upon application of the magnetic field.}
\label{fig:microstructure_viz-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_on.png} 
\caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the particle at different magnetic field strengths, $\bar{B}$, and the nematic order 
         parameter $S$ in lines. I quantify the domain size and ordering of the particles, and show that the change in both parameters are correlated with the strength of 
         the applied magnetic field.} 
\label{fig:domain_size-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/domain_size_aniso-field_on.png} 
\caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
         stabilized with magnetically responsive oblate and prolate ellipsoids. I see that upon application of the field, bijels stabilized with prolate 
         particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size 
         perpendicular to the applied field, $L_{\perp}$ decreases. The opposite is true for bijels stabilized with oblate particles. The tortuosity data 
         demonstrate that as the domain size increases, the tortuosity decreases and vice versa.} 
\label{fig:domain_size_aniso-field_on} 
\end{figure}

From Figure \ref{fig:domain_size_aniso-field_on}, domain size anisotropy is observed upon application of the field for both
particle morphologies. I also see some domain anisotropy with no applied field, which increases upon application of the magnetic field.
The directional domain sizes, $L_{\perp}$ and $L_{\parallel}$ increase by 73\% and 7\%\ respectively for oblate particles and
10\% and 44\% respectively for oblate particles. The axes that coarsens the most is consistent with past work, explained through the
directions particles reorient in response to the applied magnetic field. As particles unjam and rejam at the interface due to reorientating 
to the magnetic field, they adopt direction specific surface coverages which manifest as anistropic domains upon jamming. In Figure 
\ref{fig:domain_size_aniso-field_on}, I demonstrate that the application of the magnetic field changes the domain size.

@@

In Figure \ref{fig:particle_viz-field_on}, I see the initial configuration of particles at the monolayer show that the orientations are random and that the 
particles tend to lie flat on the interface. However, upon application of the magnetic field the particles orient to the field direction. With no applied field,
I see that the orientations and positions of the particles vary slightly for both ellipsoidal particle morphologies. This effect is due steric effects between particles,
as identified in Gunther et al. \cite{gunther_timescales_2014} I observe that for bijels stabilized by prolate ellipsoids, I see the adoption of orientational order
to the magnetic field and qualitatively different particle arrangements on the interface. These indicate that the interfacial capillary forces or steric interactions 
with other particles differ upon application of the magnetic field. The particles would prefer to lie flat on the interface to minimize the interfacial energy of 
adsorption onto the interface. Changes in the local arrangement arise from the unjamming and rejamming process upon application of the magnetic field. These differences 
in the orientational and interfacial ordering can be characterized to understand how each respective interaction force changes as a function of time.

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.3]{../figures/results/paper2/interface_angle-nint-field_on.png} 
\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q6 \rangle)$ on the left and right respectively, 
         versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. I demonstrate that upon application 
         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly between oblate and prolate ellipsoids 
         indicating that the dynamics for both particle morphologies differ. I also observe magnetic field dependence in each property for both particle types, 
         suggesting that these changes are driven primarily through the change in the applied field strength.} 
\label{fig:interface_angle-nint-field_on} 
\end{figure}

From Figure \ref{fig:interface_angle-nint-field_on}, I identify that prolate and oblate particles respond differently at the interface. For
bijels stabilized by oblate ellipsoids, I characterize an increase in $\langle \psi \rangle$ from an initial value of $19 ^{\circ}$,
before it reduces slightly and begins to increase once again. The initial starting value of $\langle \psi \rangle$ indicates the
particles are lying close to flat on the interface, before they begin to tilt out of the interface when the magnetic field is applied. Then,
$\langle \psi \rangle$ plateaus as the interface begins to move in response to the tilting particle at the interface. This is caused by the
large adsorption energy of the particles at the interface of the bijel, caused by high surface tension. Finally, the particles jam in place,
locking the interface at an angle to the particle. I see the rate of increase in $\langle \psi \rangle$ at early stages and the time spent
in the plateau increase with a larger applied magnetic field. The final angle at the interface is also dependent upon the applied field
strength.

When analyzing $\langle \psi \rangle$ for bijels stabilized by prolate particles, this behavior can also be observed. $\langle \psi \rangle$
begins at $10 ^{\circ}$. I see $\langle \psi \rangle$ increases, before plateauing and slowly decreasing. The initial peak height and rate of increase in 
$\langle \psi \rangle$ is field dependent, although given the small decrease in $\langle \psi \rangle$ it is unclear if the final value of this parameter 
is field dependent for bijels stabilized with prolate particles. The changes in $\langle \psi \rangle$ for bijels stabilized with prolate particles are 
small compared to bijels stabilized with oblate particles. I visualize this process by color coding snapshots of the particle monolayer at the initial
and final timesteps of bijels stabilized by prolate particles with a field strength of $\bar{B} = 1$ applied.

@@

I can also do the same for $\langle \psi \rangle$ and
$\langle Q6 \rangle$. A timescale derived from
$\langle \psi \rangle$ named $\tau_{\langle \psi \rangle}$
represents the capillary timescale between the interface and the
particle. Given the shape of the plot, I assign the
$\tau_{\langle \psi \rangle}$ to be the time when the first minimum of
$\langle \psi \rangle$ is observed for prolate particles and the first
maximum for oblate particles. A timescale derived from
$\langle Q6 \rangle$, named $\tau_{\langle Q6 \rangle}$ is also
calculated which represents a timescale of local particle rearrangement.
I define $\tau_{\langle Q6 \rangle}$ as the time when
\(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
minimum of $\tau_{\langle Q6 \rangle}$ for the oblate particles. I
omit \(\bar{B} = 0\) as previous results have identified the domain size
changes observed there. I then plot the average domain size $L$
against time rescaled with these three timescales in Figure
\ref{fig:domain_size-field_on-scaled}.

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/domain_size-field_on-scaled.png} 
\caption{Plots of domain size with different timescales. The top and bottom row represent the average domain size for bijels stabilized with oblate and 
         prolate particles respectively. The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, 
         $\tau_S$. The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$. 
         The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$. I show 
         that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the 
         dominating effect is steric hindrance of the particles during rearrangment at the interface.} 
\label{fig:domain_size-field_on-scaled} 
\end{figure}

In Figure \ref{fig:domain_size-field_on-scaled}, the left plot plots the
average domain size against time rescaled using $\tau_S$. The
the domain sizes do not collapse onto a single line, which is expected
if I want to explain the dynamics using the nematic order parameter.
This confirms the observation made above that the dynamics do not only
depend on the reorientation of particles to the field. The middle plot
demonstrates the average domain size against time rescaled using
$\tau_{\langle \psi \rangle}$. There is good agreement
between all simulations for prolate particles, although the point when
$\frac{t}{\tau_{\langle \psi \rangle}} = 1$ lies when the domain size
transition has started. However for oblate particles this
timescale does not describe the dynamics well.

@@

The hysteresis curve in Figured \ref{fig:hysteresis_curve} shiows that the microstructure change at higher
field strengths began to reduce with each subsequent field strength
jump, suggesting that the ordering of the particles is linked to the
domain size change observed. In the previous section, I saw that domain
size changes in bijels after jamming are constrained by magnetic field
driven local rearrangement of the particle monolayer. In this section,
I explore how pre-existing order in the particles affect the degree of
domain size change observed. I apply fields of strength
$\bar{B}_{template} = 0, 0.2, 0.5, 1$ during phase separation to
create bijels stabilized with ellipsoidal particles with pre-existing
particle order. I then apply a field strength of $\bar{B}_z = 1$ and
observe the time evolution of the system for $t = 10^5$ timesteps. I
simplify my nomenclature here for brevity. For example,
$\bar{B}_z: 0.0 \rightarrow 1.0$ represents a bijel made with no
field, and a field of $\bar{B}_z = 1.0$ applied during the simulations conducted here. 
I begin by visualizing the microstructure
changes experienced by bijels simulated with pre-existing particle order
in Figure \ref{fig:microstructure_viz-field_up}.

@@

In Figure \ref{fig:domain_size-field_up}, I define the difference
between the final and initial magnetic field strengths as
$\Delta \bar{B}$. The onset of microstructural response is observed to
be $\Delta \bar{B}$-dependent, indicating that a stronger driving
force is required to induce structural reorganization. Additionally, the
extent of microstructural change is also correlated with
$\Delta \bar{B}$, where $\Delta \bar{B} = 1$ results in average
microstructural variations of 5\% and 2\% for oblate and prolate
particles, respectively which decreases as $\Delta \bar{B}$ decreases.
I further characterize the relationship between $\Delta \bar{B}$ and
nematic order, showing that an increase in \(S\) correlates with
$\Delta \bar{B}$. This suggests that changes in domain size are
intrinsically linked to the initial particle ordering within the system.
These findings indicate that characteristic length scale evolution is
dependent on both aspect ratio and field strength variation,
highlighting the role of particle alignment in governing domain
coarsening dynamics. To further quantify the anisotropic microstructural
evolution, I define the relative change in domain size as
$\Delta L = \frac{L_{f} - L_{i}}{L_{i}}$, where $L$ represents
either $L_{\perp}$ or $L_{\parallel}$. The same formulation is
applied to the tortuosity in the respective directional components. I
do this to characterize the $\Delta \bar{B}$-dependent changes
observed in the domain anisotropy. The results are presented in Figure
\ref{fig:domain_size_aniso-field_up}.

\begin{figure} 
\centering 
\includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_up.png} 
\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with 
         oblate and prolate ellipsoidal particles starting at different particle orders. I plot these results against the change in the applied field 
         strength, $\Delta B$. I show that the anisotropic domain size is inversely correlated to the tortuosity. I see that $L_{perp}$ changes for 
         a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.} 
\label{fig:domain_size_aniso-field_up} 
\end{figure}

From Figure \ref{fig:domain_size_aniso-field_up}, domain
size anisotropy is observed upon increasing the applied field
for both particle morphologies. Some domain anisotropy with no applied field can be observed, 
which increases upon application of the magnetic field. The directional domain sizes,
$L_{\perp}$ and $L_{\parallel}$ increase by $73\%$ and $7\%$
respectively for oblate particles and $10\%$ and $44\%$ respectively
for prolate particles. The axes that coarsens the most is consistent
with past work, explained through the directions particles reorient in
response to the applied magnetic field. The
tortuosity of the bijel is initially around $\tau \approx 1.5$,
consistent with simulations of the diffusive tortuosities of gyroid
structures using Lattice Boltzmann simulations.
\cite{luo_macroscopic_2020} Upon application of the field,
$\tau_{\perp}$ slightly decreases while $\tau_{\parallel}$
increases. Consistent with past work, an increase in the domain size sees a decrease in
tortuosity in that direction. \cite{karthikeyan_formation_2024}. The results show that the
tortuosity of the bijel is noticeably affected by the application of
magnetic fields.

@@

In Figure \ref{fig:particle_viz-field_up}, I see the effect of the
application of the magnetic field on the monolayer. The initial
configuration of particles at the monolayer show that even at initial
configuration of run $\bar{B}: 0.2 \rightarrow 1$, most particles are
oriented towards the field. Upon increasing the field strength to
$\bar{B} = 1$, all particles shown can be seen to be ordered to the
field, matching the results for the nematic order parameter shown in
Figure \ref{fig:domain_size-field_up}. I also observe the alignment of
the long axis of the particles to the magnetic field, demonstrating the
origin of the microstructure anisotropy. To understand how the particle
reorientation at the interface causes microstructure reorientation I
quantify the average interface angle, $\langle \psi \rangle$ and the
local interface order of the material, $\langle Q6 \rangle$ in Figure
\ref{fig:interface_angle-nint-field_up}.

@@

Figure \ref{fig:interface_angle-nint-field_up} shows that
prolate and oblate particles respond differently at the interface upon application of a magnetic field
even with pre-existing ordering of the particles. I
show that there are three time evolution trends for
$\langle \psi \rangle$ and $\langle Q6 \rangle$ for both oblate and
prolate particles despite the differences in the initial state of the
particles. In oblate particles $\langle \psi \rangle$ begins closer to
$20 ^{\circ}$ as the axis of symmetry lies close to the interface
normal. For bijels experiencing a field strength history of
$\bar{B}: 0 \rightarrow 1$ and $\bar{B}: 0.2 \rightarrow 1$,
$\langle \psi \rangle$ increases, plateaus and increases again before
plateauing again. This is indicative of particles tilting at the
interface, before interfacial capillary interactions ``pause'' particle
reorientation before the applied magnetic field begins to cause
particles to tilt out of the interface. I see similar trends for bijels
stabilized by prolate particles. $\langle \psi \rangle$ begins near
$11 ^{\circ}$. I see a decrease before reorientation ceases, and
finally $\langle \psi \rangle$ increases again.

When looking at $\langle Q6 \rangle$ for $\bar{B}: 0 \rightarrow 1$
and $\bar{B}: 0.2 \rightarrow 1$ for oblate particles, I see that the
trends are similar with an initial decrease, followed by a plateau and
increase over time before plateauing again. $\langle Q6 \rangle$
generally decreases with a large decrease observed for
\(\bar{B}: 0 \rightarrow 1\) from an initial hexagonally packed system
to a structure that is locally ordered but not close packed. $\langle Q6 \rangle$ increases before plateauing 
in both systems around 5000 timesteps. The significance of
this time is unknown for $\bar{B}: 0.2 \rightarrow 1$ but for
$\bar{B}: 1 \rightarrow 1$, this is approximately the local
crystallization point when $\langle Q6 \rangle \geq 0.38$.
